\cvsection{Experience}
\begin{cventries}
  \cventry
    {Research Assistant}
    {Rutgers University}
    {New Brunswick, New Jersey}
    {May 2019 - August 2019}
    {
      \begin{cvitems}
        \item {Responsible for development of a new database entry system to track ongoing experiments.}
        \item {Conducted research in the Hybrid Micro/Nanomanufacturing Laboratory developing ionic thrusters for propulsion systems of small satellites.}
        \item {Investigated fabrication for wafer-scale arrays of hierarchical micro/nanostructures using photolithography.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
  \cventry
    {Database Programmer}
    {MobileArq}
    {Summit, New Jersey}
    {Oct. 2014 - Sept. 2018}
    {
      \begin{cvitems}
        \item {Managed databases for 40,000 families using SQL scripts.}
        \item {Created websites for various organizations including the Summit Tennis Club using a LAMP Stack and WordPress.} 
        \item {Designed mockups and wireframes for a mobile application to assess otolaryngology residents at Columbia University.}
      \end{cvitems}
    }
  \cventry
    {Bid Estimator}
    {Tomkin Company}
    {Scotch Plains, New Jersey}
    {Mar. 2017 - Sept. 2017}
    {
      \begin{cvitems}
        \item {Created bid estimates for numerous construction projects throughout New York and New Jersey based upon review and analysis of hundreds of Architectural, Structural, and Electrical drawings.}
        \item {Collaborated with high profile construction companies to accommodate for varying project requirements to produce accurate estimates.}
      \end{cvitems}
    }
  \cventry
    {Volunteer}
    {NJSTEM}
    {Summit, New Jersey}
    {Feb. 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Led children through the basics of how to solder and assemble basic circuits through a program named, “Soldering Sundays”.}
      \end{cvitems}
    }
    \vspace{-2mm}

    
\end{cventries}
