\cvsection{Extracurricular Activities}
\begin{cventries}
    \cventry
        {Robotics Engineer}
        {Robojackets Robonav}
        {}
        {}
        {
          \begin{cvitems}
            \item {Tasked with building an autonomous robot capable of off-road navigation in varying weather and lighting conditions.}
                    \vspace{1mm}
            \item {Used OpenCV to implement a line detection algorithm able to identify lane lines and barrels posing as obstacles.}
                    \vspace{1mm}
            \item {Learned and implemented basic LiDAR mapping, path planning, and computer vision systems with ROS and C++.}
                    \vspace{1mm}
            \item {Contributed to codebase with over 30,000 lines of code and utilized CI/CD workflow.}
                    \vspace{1mm}
          \end{cvitems}
        }
        \vspace{-1mm}
    \cventry
        {Simulation Subteam}
        {Automotive Lidar Vertically Integrated Project}
        {}
        {}
        {
          \begin{cvitems}
            \item {Tasked with developing a scanning LiDAR system implemented on an RC vehicle to enable point-to-point autonomous navigation, with collision avoidance using ROS, Python, and C++.}
                \vspace{1mm}
            \item {Improved the existing vehicle and world simulation to test already written code and to eliminate bugs before running code on the physical vehicle.}
                \vspace{1mm}
            \item {Creating new gazebo simulations, such as moving obstacles, to test the robustness of our algorithms.}
                \vspace{1mm}
          \end{cvitems}
        }
        \vspace{-1mm}
  \cventry
    {Hackathons and More}
    {Projects}
    {}
    {}
    {
      \begin{cvitems}
        \item {Too Long Didn't Listen (TL:DL): Created a tool during HackGT 2019 to convert an mp3 file into a summarized version of the audio, highlighting keywords and linking selected phrases.}
            \vspace{1mm}
        \item {Created a voice assistant during the HackNYU 2018 hackathon to recognize toxic language and depression using machine learning.}
            \vspace{1mm}
        \item {Created a Fantasy Premier League tool to accurately predict player performances using machine learning in Python.}
             \vspace{1mm}
        \item {Created a basic aimbot in Counter-Strike: Global Offensive using C and x86 Assembly.}
            \vspace{1mm}
        \item {Modeled local weather data using Python to view differences in weather patterns in the past decade.}
            \vspace{1mm}
        % \item {Hands-on security projects for mitigating against SQL injection, cross site scripting, and ensuring least privilege access as part of Greyhat Cybersecurity Club.}
        % \item {Programmed with Drupal open source libraries, and collaborated with developers around the world during the Google Code-in.}
        %     \vspace{1mm}
        % \item {Experience building and flying autonomous planes and drones using open autopilot software: \href{https://bit.ly/2lxEIyN}{https://bit.ly/2lxEIyN}}
        %\item {Robotics Club at the Union County Vocational Technical School (UCVTS). Created a viable robot to compete in various competitions and events.}
        %\item {Experimented with supervised and unsupervised learning as well as algorithm chains.}
        % \item {Used R to model simple linear regression, multiple linear regression, ANOVA, MANOVA, and time series.}            \vspace{1mm}
      \end{cvitems}
    }
    % \cventry
    %     {Georgia Tech GreyHat Club}
    %     {Cybersecurity}
    %     {}
    %     {}
    %     {
    %       \begin{cvitems}
    %         \item {Created a basic aimbot in Counter-Strike: Global Offensive using C and x86 Assembly.}
    %              \vspace{1mm}
    %         % \item {Won the Equifax CTF challenge at HackGT 2019 with the Greyhat team. Competed in PicoCTF hosted by Carnegie Mellon University.}
    %         %      \vspace{1mm}
    %         \item {Hands-on security projects for mitigating against SQL injection, cross site scripting, and ensuring least privilege access as part of Greyhat.}
    %       \end{cvitems}
    %     }
    % \vspace{-1mm}
\end{cventries}


